Constraints on the masses of substructures in $x$ lens galaxies

### 2016-11-16 doc/Paper2/ms.tex
Sections
Center for eResearch

\section*{Acknowledgements}
It is a pleasure to thank Matt Auger (Cambridge) for valuable discussion and
providing the data. Barkana

This work was funded by a Marsden Fast Start grant from the Royal Society of
New Zealand.

>>>>

\section{Einstein Ring 0047-2808}

\section{The Jackpot}

\section{Cosmic Horseshoe HST Image}

\section*{Acknowledgements}
It is a pleasure to thank Matt Auger (Cambridge) for valuable discussion and
providing the jackpot data. Barkana

This work was supported by a Marsden Fast Start grant from the Royal Society of
New Zealand. We also made use of resources provided by the Centre for
eResearch at the University of Auckland.
